% Data Frame documentation

\begin{verbatim}
from nmea import data_frame
\end{verbatim}

\subsubsection{DataFrame}

Contains a snapshot of GNSS data. \\

\textbf{Function List}

\begin{itemize}
	\item \textbf{\_\_init\_\_(fix=None, gnss=None, active=None, inview=None, rmc=None, latlon=None, vel=None)}

		All arguments provided to the \emph{DataFrame} constructor are optional and default to None.

		\paramslist{
			fix & \emph{NMEAFixMessage} & GGA Message \\
			gnss & \emph{GNSSFixData} & GNS Message \\
			active & \emph{NMEADOPActiveSatsMessage} & GSA Message \\
			inview & List[\emph{NMEASatsInviewMessage}] & GSV Message \\
			rmc & \emph{NMEARMCMessage} & RMC Message \\
			latlon & \emph{NMEALatLonMessage} & GLL Message \\
			vel & \emph{NMEAVelocityMessage} & VTG Message
		}
	
	\item \textbf{get\_next\_frame} \classmethod

		Capture an entire data frame from a NMEA input stream. This function does not handle errors decoding
		NMEA sentences, so a \emph{ValueError} may be thrown from inside. It is suggested this function is surrounded
		in a try/except block that explicitly handles \emph{ValueError}.
		
		\paramslist{
			stream & \emph{GenericInputStream} & Input stream to receive sentences from \\
			debug & bool & Indicate to dump NMEA to console. Default false.
		}

	\item \textbf{push\_back\_message}

		Add a message to the data frame.

		\paramslist{
			msg & \emph{NMEAMessage} & An instance of a message
		}

\item \textbf{is\_complete} \returns{bool}

		Determine if the data frame had all necessary variables filled.

\end{itemize}

\proplist{
		gps\_time & str & UTC date and time of fix \\
		velocity & float & Velocity at fix \\
		track & float & Direction of travel \\
		latitude & float & Latitude of fix \\
		longitude & float & Longitude of fix \\
		altitude & float & Altitude of fix \\
		fix\_quality & str & Fix quality in the \emph{NMEAFixMessage} \\
		nsats & int & Number of satellites used to calculate fix \\
		sv\_observations & List[\emph{SVObservation}] & All satellite observations at the moment \\
		all\_messages & List[\emph{NMEAMessage}] & List of all contained NMEA Messages
}

